The title

### 2016-10-18 analysis/paper/paper.Rmd
Landscape observations

- our landscape observations
- descriptions of existing cuttings that we visited
- GPS data from transect
- surface finds of artefacts by KK

>>>>

### Landscape observations

The landscape in the Lower Irrawaddy region is characterized by river terraces that are heavily incised. The uppermost terrace T1 is only sparsely preserved with one relict hill where the Chinthaungma monastery sits 70 m above the river level. Thick red gravel layers with a reddish-brown silty sand matrix overly the bedrock.

Terrace 2 (T2) can be distinguished by the scarcity of vegetation compared to the lower terrace 3 (T3). Probably due to the very thin or absent soil layer on top pf the bedrock, only grass, shrubs and some scattered trees grow on T2. The terrain is severely incised and has a lot of gently rolling gullies and valleys.

On T3, the vegetation is more prominent and there are fewer incisions. The red gravel layer is not as dominant as in T1, whereas the soil layer seems to be more pronounced. There are some filled fields and a golf course that was created in 1947 for the local oil workers. Because of its lower location, the gravels may be colluvial redposits from T1, although it could be an alluvial terrace.

- descriptions of existing cuttings that we visited
- GPS data from transect
- surface finds of artefacts by KK
